\begin{abstract}
Large language models (LLMs) are increasingly used as scoring and
representation engines for recommendation, yet comparisons across LLM-based
recommenders are often confounded by different candidate sets, backbones,
importers, and evaluation schemas. We first contribute a rigorous unified
same-candidate reranking protocol: every method ranks the same 101 candidates
(one positive and 100 popularity-sampled negatives) for each of 10{,}000 users,
uses the same Qwen3-8B backbone when an LLM is required, and is evaluated with a
shared importer, identical metrics, exact coverage checks, and paired
Holm-corrected bootstrap tests, with full provenance. Against eight
official-code-level LLM-based recommendation baselines across eight Amazon
domains (Beauty, Books, Electronics, Movies, Sports, Toys, Home, Tools), our
central empirical finding is that a \emph{task-grounded pointwise LLM relevance
posterior} -- the model's own per-candidate relevance probability, used directly
as the ranking score -- ranks first in six of the eight domains, improving
NDCG@10 by $+21.6\%$ to $+53.2\%$ over the strongest baseline (leading on all
seven metrics HR@5/@10/@20, NDCG@5/@10/@20, MRR in five of these six domains ---
Electronics, Sports, Toys, Home, Tools; 56/56 paired-significant --- and on six
of seven on Books, HR@20 versus LLMEmb the exception). In the remaining two
domains it is not first: rank~2 on Beauty ($-11\%$ NDCG@10 behind ProEx, though
this shortfall is not Holm-significant on any metric, leaving \method{}
statistically indistinguishable from the strongest baseline) and mid-pack at
rank~5 on Movies ($-24\%$ behind LLMEmb, substantially behind the stronger
baselines). We report these two losses explicitly rather than
dropping them. We compute paired Holm-corrected bootstrap tests on all eight
domains: on the six winning domains \method{} is significantly ahead on all 56
metric/baseline pairs (54/56 on Books), while on Movies it is significantly
behind the stronger baselines on 22 of 56 pairs. As a first cross-family test of
whether the advantage is specific to the unified Qwen3-8B backbone, we re-run the
identical pipeline with a second, different-family LLM (Llama-3.1-8B-Instruct) on
the four new winning domains: the rank-first NDCG@10 result replicates in all four
($+11.0\%$ to $+21.4\%$ over the strongest baseline), at a $12$--$17\%$ lower
absolute level that tracks backbone quality.

We then report a rigorous \emph{negative result} on the design space this work
set out to study. We instrument the pointwise posterior with a principled
calibrated-uncertainty and risk-adjusted ranking family that decomposes
uncertainty into boundary ambiguity, a calibration gap, evidence support, and
counterevidence. Under a leave-one-component-out ablation and a
raw-probability attribution, this machinery does not improve same-candidate
ranking: the zero-risk setting is test-best in all four diagnostic domains, a
confidence-only variant matches or exceeds the full family in three of those
four domains, and individual uncertainty terms are inert or mildly harmful. The
working ranking signal lies in the posterior itself, not in the
uncertainty decomposition. As a minor, descriptive observation -- and one we
caveat as partly circular -- the event-level uncertainty signal does stratify
reliability, but we do not claim it improves ranking. This is a scoped result
about same-candidate reranking, not a full-catalog recommender SOTA claim.
\end{abstract}
