\section{Discussion}
\label{sec:analysis}

\subsection{Why Same-Candidate Reliability Matters}

Many deployed recommenders use a multi-stage architecture: an upstream retriever
generates a candidate set, and a downstream ranker or reranker orders those
candidates. Our experiments target the second stage. This scope is narrower
than full-catalog recommendation, but it is also where LLM-based scoring is
most commonly used because evaluating every catalog item with an LLM is
expensive.

The same-candidate protocol makes this claim auditable. Since all methods rank
the same candidate rows, performance differences cannot be explained by a
different candidate generator. Since all methods are imported through the same
metric code, the comparison is not mixing native full-catalog metrics with
reranking metrics. This is also the setting in which we can cleanly test whether
the uncertainty decomposition adds anything to the underlying pointwise
posterior, and---as the diagnostics below show---measure exactly where the
ranking signal lives.

\subsection{What the Diagnostics Say}

The diagnostics support a careful and, we think, scientifically informative
interpretation. The headline gain comes from a single, simple signal: the
task-grounded pointwise relevance posterior, used directly as the ranking score
(\S\ref{sec:results}). The uncertainty machinery layered on top of it---boundary
uncertainty, calibration-gap, counterevidence, and risk penalty---does not add
ranking utility in the same-candidate setting. Boundary uncertainty is exactly
inert, removing counterevidence or the risk penalty is nonworse on NDCG@10, the
test-best risk exponent is zero in all four domains, and a raw-probability
attribution shows that ranking on the posterior alone matches the full
configuration to within a few thousandths of NDCG@10. The observation module
shows separately that high uncertainty corresponds to lower ranking reliability,
but because events are binned by the method's own uncertainty and the score is a
monotone function of the same posterior, this is a descriptive (and partly
mechanical) reliability stratification, not evidence that the uncertainty term
improves ranking.

We read this as a clean negative result worth stating plainly rather than
hiding. The actionable signal that a calibrated-uncertainty decomposition was
designed to surface is, for same-candidate ranking, already captured by the
pointwise posterior itself; the decomposition is therefore best understood as an
analyzed design space whose components we have measured and found inert for
ranking, not as a validated source of the improvement. This is a more honest
and more useful contribution than an unsupported claim that uncertainty
decomposition drives the gain: it tells future work where the signal actually
lives, and it cautions against adding risk/uncertainty terms to a ranking score
without measuring their effect. The uncertainty signal may still be valuable as
a reliability descriptor or for downstream abstention/deferral decisions, which
we leave to future work.

\subsection{Limitations}

\begin{enumerate}
    \item \textbf{No full-catalog claim.} We evaluate controlled reranking over
    101 candidates per user. Candidate generation and full-catalog retrieval
    remain future work.
    \item \textbf{Two additional backbones tested; broader model coverage open.}
    The formal main comparison uses a unified Qwen3-8B backbone across all eight
    Amazon-domain same-candidate tasks (with the uncertainty diagnostics run on
    four of them). To test whether the same-candidate ranking advantage survives
    frozen-model substitution, we re-ran the identical C-CRP scoring pipeline
    under two additional different-family LLMs --- Llama-3.1-8B-Instruct and
    Mistral-7B-Instruct-v0.3 --- across all eight domains
    (\S\ref{sec:second_backbone}): the headline NDCG@10 rank-first result clears
    the strongest official baseline in $17$ of $18$
    backbone$\,\times\,$(winning-domain) cells (Mistral in all six, Llama in five;
    Llama-Books a $1.0\%$ near-miss vs.\ LLMEmb), with the official baselines held
    at their unified-Qwen comparison values; the absolute level is consistent with
    backbone capability ($\sim 10$--$25\%$ lower). The Beauty/Movies losing
    direction also transfers to both additional backbones. This establishes
    cross-family transfer of the win/loss partition under frozen-model
    substitution; we have not tuned baselines per-backbone (a re-tuned
    cross-backbone SOTA comparison is left to future work), and other LLMs,
    catalogs, or retriever distributions may still change calibration and
    uncertainty behavior.
    \item \textbf{Descriptive uncertainty diagnostics.} The observation module
    shows that uncertainty stratifies reliability, but it is not a causal
    intervention. It does not prove that changing uncertainty alone would change
    ranking utility.
    \item \textbf{Uncertainty decomposition is inert for ranking.} The
    leave-one-component-out diagnostics and the raw-probability attribution show
    that the calibrated-uncertainty and risk-adjusted terms do not improve
    same-candidate ranking over the pointwise posterior they are built on; the
    test-best risk exponent is zero in all four domains. The paper therefore
    claims that a task-grounded pointwise relevance posterior ranks first under
    the controlled same-candidate protocol, and reports the uncertainty
    decomposition as a characterized negative result plus a descriptive
    reliability signal---not as a validated ranking-improvement mechanism.
    \item \textbf{External adapter policy.}\label{lim:backbone} We preserve
    official-code-level
    baseline mechanisms and use a shared Qwen3-8B representation bridge for
    same-candidate scoring. This gives a fair controlled comparison, but it is
    not the same claim as reproducing each method under its original full-catalog
    serving stack. A bridge-fidelity check (\S\ref{sec:results}) finds the
    Qwen3-8B bridge recovers $\approx\!90\%$ of LLM2Rec's native same-candidate
    NDCG@10 (Tools $110\%$, Sports $78\%$), so the bridge does not collapse
    baselines to the floor; we have not, however, run a native-backbone
    reproduction for every baseline.
    \item \textbf{Exploratory gap decomposition.} Our analysis of why \method{}
    wins on six domains but not Beauty or Movies relates the per-domain NDCG@10
    gap to interpretable domain features (Table~\ref{tab:gap_decomposition}).
    With only eight domains these are exploratory, descriptive associations, not
    causal claims: no single feature remains significant once the number of
    features tested is accounted for, and no feature separates both non-winning
    domains. Two measurement confounds further limit the Movies row in
    particular: only $\approx\!51\%$ of its candidate items have title metadata,
    which itself handicaps a text-grounded scorer, and its history-length
    feature uses an all-user interactions proxy (a different source) because the
    evaluation panel was pruned for storage. We therefore present the
    decomposition as motivating analysis, not a validated mechanism.
    \item \textbf{LLM cost and latency.} \method{} relies on task-grounded LLM
    evidence before score export. The current paper audits ranking quality and
    evidence integrity, but it does not optimize serving latency, token cost, or
    online batching.
    \item \textbf{Prompt and parser dependence.} The signal rows are
    fail-closed and source-audited, yet they still depend on the chosen prompt,
    output schema, and parser. Different prompt templates may change
    calibration and evidence-support behavior.
    \item \textbf{Sampled negative candidate sets.} The same-candidate protocol
    uses one positive and 100 sampled negatives per event. This is appropriate
    for controlled reranking, but conclusions may differ under larger or
    retriever-generated candidate pools.
\end{enumerate}
