\section{Experiments}
\label{sec:experiments}

\subsection{Experimental Setup}

\paragraph{Datasets and Candidate Protocol.} We evaluate on eight Amazon
product-review domains: Beauty, Books, Electronics, Movies, Sports, Toys, Home,
and Tools. Each domain uses a 101-candidate same-candidate task with 10,000 test
users, except Beauty, whose smaller catalog yields 973 eligible test users.

\begin{table}[h]
\centering
\small
\caption{Dataset statistics. All domains use the same 101-candidate
same-candidate task (one positive, 100 popularity-sampled negatives); Beauty has
a smaller test-user pool because of its catalog size.}
\label{tab:datasets}
\begin{tabular}{lrrr}
\toprule
Domain & Test Users & Candidates/User & Candidate Rows \\
\midrule
Beauty & 973 & 101 & 98,273 \\
Books & 10,000 & 101 & 1,010,000 \\
Electronics & 10,000 & 101 & 1,010,000 \\
Movies & 10,000 & 101 & 1,010,000 \\
Sports & 10,000 & 101 & 1,010,000 \\
Toys & 10,000 & 101 & 1,010,000 \\
Home & 10,000 & 101 & 1,010,000 \\
Tools & 10,000 & 101 & 1,010,000 \\
\bottomrule
\end{tabular}
\end{table}

Each test instance consists of one ground-truth next item and 100 negatives.
The same candidate rows are shared by all methods; no method receives a
different negative set or a different candidate order as an advantage. The
positive item is hidden from the scoring prompt and from the baseline scoring
wrappers. Validation rows are used only for selection or calibration decisions
declared in advance, while test rows are reserved for final reporting and
paired tests.

The task package keeps validation and test artifacts separate. Each domain has
train-history files for the corresponding task split, validation ranking rows
for selection, test ranking rows for final reporting, and a test
\texttt{candidate\_items.csv} file that defines the exact key set every
paper-facing score file must cover. This separation prevents validation
selection code from silently reading test histories and prevents a method from
entering the table with a different candidate universe.

A result is table-eligible only if its score file exactly matches the candidate
key set, has no duplicate or missing keys, contains finite numeric scores, and
passes the local/server provenance checks. The score contract is deliberately
minimal:
\[
(\texttt{source\_event\_id},\texttt{user\_id},\texttt{item\_id},\texttt{score}).
\]
This contract lets official baselines keep their native training objective
while forcing their final candidate scores through the same metric code.

\paragraph{Backbone and Fairness Policy.} All methods use Qwen3-8B whenever an
LLM or LLM-derived representation is required. Baseline-specific adapters,
checkpoints, graph modules, intent modules, or representation learners are
preserved when they are part of the official algorithm. We do not retune every
baseline on the test split; the primary comparison uses official default or
recommended baseline hyperparameters, while \method{} uses fixed or
validation-controlled settings. Full-catalog metrics reported by upstream
repositories are not imported into the paper table.

\paragraph{Baselines.} In every domain we compare against the same eight
official-code-level LLM-based recommendation baselines:

\begin{itemize}
    \item \textbf{ELMRec}~\cite{elmrec}: High-order interaction-aware LLM recommendation
    \item \textbf{IRLLRec}~\cite{irllrec}: Intent representation learning with LLMs
    \item \textbf{LLM2Rec}~\cite{llm2rec}: LLM embedding with sequential recommendation
    \item \textbf{LLMEmb}~\cite{llmemb}: LLM-generated embeddings for recommendation
    \item \textbf{LLM-ESR}~\cite{llmesr}: LLM-enhanced long-tailed sequential recommendation
    \item \textbf{ProEx}~\cite{proex}: Profile extrapolation with LLMs
    \item \textbf{ProMax}~\cite{promax}: LLM-derived profiles with distribution shaping\footnote{ProEx and ProMax are concurrent/forthcoming works from the ProRec line; we include them as strong recent profile-based baselines and adapt their official code under our unified protocol.}
    \item \textbf{RLMRec}~\cite{rlmrec}: Representation learning with LLMs
\end{itemize}

Baselines use official default or recommended hyperparameters unless a
documented bridge is required by the unified protocol. Each row must record the
official repository, pinned commit, adaptation mode, checkpoint or
representation artifact when applicable, score path, score hash, and coverage
audit. Test-set model selection is forbidden for both baselines and \method.

\input{tables/baseline_provenance_summary}

\paragraph{Metrics and Statistics.} We report HR@$k$ and NDCG@$k$ for
$k\in\{5,10,20\}$, plus MRR. The paired unit is the user event: for each
method and metric, we compare the per-event score of \method{} with the
corresponding per-event score of an official baseline. For each domain,
\method{} is compared against each official baseline on all seven metrics,
yielding 56 paired tests (8 baselines $\times$ 7 metrics). We use paired
event bootstrap confidence intervals with 2,000 bootstrap samples, 95\%
percentile intervals, and Holm correction at $\alpha=0.05$ over the full
family of 56 tests in that domain. The Holm-corrected paired-test gate is
reported for the four domains where \method{} ranks first on every metric
(Sports, Toys, Home, Tools); for the four original domains we report ranks and
per-metric improvements directly.

\paragraph{Evidence Packaging.} Every completed row has a lightweight local
evidence package with metrics, row counts, provenance, score audits, logs, and
server manifest hashes. Large score files, prediction files, checkpoints, and
embeddings remain server-side unless an archive decision requires otherwise.
This separation keeps the GitHub artifact small while preserving enough hashes
and row counts to detect missing or accidentally cleaned evidence. The
paper-facing ledger contains 72 rows: 64 official baseline rows (eight
baselines $\times$ eight domains) and eight \method{} rows.

\paragraph{Diagnostic Modules.} The main comparison is accompanied by three
paper-critical diagnostics, run on the four domains (Sports, Toys, Home, Tools)
for which the full per-event signal rows are packaged locally. The observation
module bins events by C-CRP uncertainty and checks whether higher uncertainty
corresponds to lower ranking reliability. The component module evaluates
leave-one-component-out variants under the frozen same-candidate protocol. The
hyperparameter module sweeps real controls, especially $\eta$ and the
uncertainty weight grid, with validation-only selection and reporting-only test
curves. These diagnostics are not allowed to replace the main official-baseline
comparison.

\subsection{Main Results}

\input{tables/main_results}
