\section{Related Work}
\label{sec:related}

\subsection{LLM-Based Recommendation}

The integration of large language models into recommendation systems has followed several paradigms. \textbf{Embedding-based methods} such as LLMEmb~\cite{llmemb} extract item representations from LLM hidden states and compute similarity scores. \textbf{Sequential methods} like LLM2Rec~\cite{llm2rec} and LLM-ESR~\cite{llmesr} combine LLM features with sequential models (SASRec~\cite{sasrec}) for next-item prediction. \textbf{Profile-based methods} including ProEx~\cite{proex} and ProMax~\cite{promax} leverage LLMs to generate user profiles that guide recommendation. \textbf{Graph-enhanced methods} such as ELMRec~\cite{elmrec} and RLMRec~\cite{rlmrec} combine graph collaborative signals with LLM reasoning.

While these methods demonstrate the versatility of LLMs for recommendation, they share a common limitation: none explicitly addresses the calibration quality of their scoring outputs. Our work is orthogonal to architectural choices — we focus on \emph{how} the LLM is prompted to produce scores, which can be applied to any LLM-based recommender.

\subsection{Confidence and Calibration in Neural Networks}

Calibration of neural network predictions has been extensively studied~\cite{guo2017calibration, niculescu2005predicting}. Post-hoc methods such as temperature scaling~\cite{guo2017calibration}, Platt scaling~\cite{platt1999probabilistic}, and isotonic regression~\cite{zadrozny2002transforming} can improve calibration without retraining. However, these methods assume access to a held-out calibration set and primarily improve Expected Calibration Error (ECE) without necessarily improving discriminative performance (AUROC).

In the LLM era, calibration of verbalized confidence has been studied for question answering~\cite{kadavath2022language, tian2023just} and factual knowledge~\cite{lin2022teaching}. These works find that LLMs can be prompted to output calibrated probabilities for factual questions. We extend this finding to the recommendation domain, where the ``question'' is whether a user will interact with a specific item.

\subsection{Uncertainty in Recommendation}

Uncertainty quantification for recommendation has been explored through Bayesian approaches~\cite{zhang2020bayesian}, ensemble methods~\cite{mcauley2012learning}, and conformal prediction~\cite{angelopoulos2021gentle}. However, these methods typically require model modifications or multiple forward passes. Our approach achieves calibrated uncertainty \emph{for free} — the probability estimate is a natural byproduct of the scoring prompt, requiring no additional computation.

\subsection{Knowledge Distillation and Preference Learning}

Knowledge distillation~\cite{hinton2015distilling} transfers capabilities from a large teacher model to a smaller student. In recommendation, this paradigm has gained traction as LLMs demonstrate strong zero-shot ranking ability but remain too expensive for production serving. PEAPOD~\cite{peapod2024} distills personalized preferences from LLM outputs into compact generative recommenders. Bidirectional KD~\cite{bidirectional_kd2025} enables mutual learning between LLMs and sequential models. Rank-DistiLLM~\cite{rankdistillm2024} distills LLM ranking knowledge into cross-encoders for efficient re-ranking. Beyond simple output matching, DRDO~\cite{drdo2024} jointly optimizes reward distillation and preference alignment.

Parameter-efficient fine-tuning via LoRA~\cite{hu2022lora} offers an alternative path: rather than distilling into a separate architecture, one can specialize the LLM itself through low-rank adaptation. Multi-Scale LoRA~\cite{multiscale_lora2025} explores rank allocation strategies for recommendation tasks, while mechanistic analysis~\cite{mechanistic_lora2025} reveals how LoRA adapters modify attention patterns for reranking. The gap between LLM and traditional recommender performance can also be closed from the other direction — \citet{empowering_seq2024} show that sequential models with LLM-derived training signals approach LLM-level accuracy.

Our SRPD method occupies a distinct position: we use the base LLM's own ranking as a \emph{structured preference signal} to train domain-specific LoRA adapters. Unlike standard distillation that transfers from a larger to a smaller model, SRPD distills from the model's \emph{zero-shot ranking behavior} back into itself via supervised fine-tuning, creating a self-improving loop that preserves the model's generative capabilities while specializing its ranking preferences.

\subsection{Prompt Engineering for Recommendation}

Recent work has explored various prompting strategies for LLM-based recommendation~\cite{wang2023recmind, dai2023uncovering}. Most focus on improving ranking accuracy through better context formatting or chain-of-thought reasoning. Our contribution is distinct: we show that the \emph{output format} (asking for a probability with justification) is more important than the input format, and that this simple change simultaneously improves both ranking and calibration.
