\section{Results and Diagnostics}
\label{sec:results}

\subsection{Main Same-Candidate Comparison}

Table~\ref{tab:main_results} reports the main result across all eight domains.
\method{} ranks first in six of the eight domains. Over the strongest official
baseline, it improves NDCG@10 by +21.6\% on Books, +53.2\% on Electronics,
+29.7\% on Sports, +32.2\% on Toys, +41.0\% on Home, and +43.3\% on Tools; in
these six domains the same pattern holds for HR@5/@10/@20, NDCG@5/@10/@20, and
MRR (the lone exception is Books HR@20, where LLMEmb's deeper recall edges
\method{}). In the remaining two domains \method{} is competitive but not
first: on \textbf{Beauty} it is rank~2 of nine, trailing ProEx by $-11.0\%$
NDCG@10 ($0.1341$ vs.\ $0.1506$), and on \textbf{Movies} it is rank~5 of nine,
trailing LLMEmb by $-24.2\%$ ($0.1281$ vs.\ $0.1690$). We report these two
losses explicitly; restricting the table to the six winning domains would
overstate the method. Table~\ref{tab:improvement_over_strongest} gives the full
per-domain per-metric improvement over the strongest baseline, including the
negative Beauty and Movies deltas, and Table~\ref{tab:ccrp_rank_by_metric}
gives the per-metric ranks.

The complete evidence ledger contains 72 method-domain rows: eight official
baseline rows and one \method{} row for each of the eight domains. Every row has
10,000 users (Beauty 973), 101 candidates per user, score coverage 1.0, and the
expected row counts. For the four domains with full per-event signal rows
(Sports, Toys, Home, Tools), the paired test family contains 56 comparisons
(eight baselines times seven metrics) and all 56 deltas are positive and
Holm-significant in every one of them. Table~\ref{tab:significance_summary}
summarizes that paired-test gate, and Table~\ref{tab:full_official_ndcg10}
shows the complete per-domain NDCG@10 ranking over all eight official baselines
plus \method{} for all eight domains.

This supports a controlled reranking claim. It does not establish full-catalog
recommendation SOTA because candidate generation is not evaluated here.

\paragraph{Why the posterior wins on six domains but not Beauty or Movies.} We
read the two non-winning domains as informative rather than as noise, and offer
the following analysis---hypothesized from domain characteristics, not proven by
a controlled intervention. The six domains where the pointwise posterior wins
are ones in which a strong general-purpose LLM can recover user-conditional
relevance directly from item text and short histories. Beauty and Movies share
two properties that work against a text-only pointwise scorer and in favour of
the baselines that beat it. First, both are comparatively
\emph{popularity- and taste-skewed}: Movies in particular has heavy blockbuster
concentration and strong collaborative signal, which is exactly what LLMEmb's
trained embeddings and ProEx's profile module capture and what a per-candidate
text posterior does not. Second, both have \emph{denser, more homogeneous
candidate descriptions} (cosmetics variants; films within a genre) where 101
sampled items are textually close, so the LLM's per-candidate relevance gap is
small and easily dominated by a learned collaborative ranker. Beauty also has
by far the smallest test pool (973 users), so its margins are the least
stable. Consistent with this, the methods that beat \method{} are precisely the
embedding/profile baselines (LLMEmb on Movies, ProEx on Beauty) rather than the
floor-level generative or graph baselines. We therefore frame the result as: a
directly elicited pointwise LLM posterior is the strongest single reranking
signal in most domains we tested, but it does not subsume trained collaborative
structure in popularity-skewed, text-homogeneous catalogues. We flag this as
analysis to motivate future hybridization, not as a validated causal claim.

\paragraph{Attribution: the win is the pointwise posterior.} We are explicit
about which signal produces the headline ranking. The reported \method{} rows
in Table~\ref{tab:main_results} are obtained by ranking the 101 same candidates
by the raw task-grounded LLM relevance probability $\hat{p}$ alone---a pointwise
posterior per candidate---ranked descending with a fixed seeded tie-break. The
calibrated/uncertainty/risk-adjusted machinery is not what carries the gain.
Two pieces of evidence support this (computed on the four diagnostic domains
with full per-event signal rows). First, the leave-one-component-out summary
(Table~\ref{tab:ablation_ndcg10}) shows the uncertainty terms are inert or
redundant for ranking: boundary uncertainty is exactly inert in 4/4 domains,
and removing counterevidence or the risk penalty is nonworse in 4/4 domains on
NDCG@10. Second, a raw-probability attribution ablation
isolates the posterior directly. Holding the candidate rows, importer, and
seeded tie-break fixed, ranking by $\hat{p}$ alone tracks the reported \method{}
NDCG@10 within $\le 0.008$ across the three domains with local signal rows
(raw-$\hat{p}$ minus reported NDCG@10: $-0.0081$ on Sports, $+0.0024$ on Home,
$+0.0038$ on Tools). On the matched selector route, a calibrated
confidence-only variant that zeroes out the uncertainty and risk terms is
nonworse than the full configuration in at least 3 of 4 domains
(e.g.\ NDCG@10 $0.2287$ vs.\ $0.2281$ on Sports, $0.1374$ vs.\ $0.1364$ on Home,
$0.1711$ vs.\ $0.1695$ on Tools). We therefore attribute the headline result to
the task-grounded pointwise relevance posterior itself, and treat the
uncertainty decomposition as an analyzed---and for ranking, inert---design space
rather than the source of the gain. We make no claim that the posterior is
calibrated in the reliability-diagram sense; ``calibrated'' here refers to the
self-reported probability target of the scoring prompt, not to a measured
expected-calibration-error guarantee.

\input{tables/significance_summary}
\input{tables/ccrp_rank_by_metric}
\input{tables/improvement_over_strongest}
\input{tables/full_official_ndcg10_ranking}

\paragraph{Reading the absolute scale.} Several official baselines sit close to
the random-ranking floor in Table~\ref{tab:full_official_ndcg10} (analytical
NDCG@10 $\approx 0.045$ for one positive among 101 candidates). This is expected
rather than anomalous. The unified protocol holds the backbone (Qwen3-8B), the
candidate set, and the score schema fixed for \emph{every} method, which removes
the native advantages of approaches whose value lies outside same-candidate
reranking: ELMRec is officially a T5 generative recommender bridged to Qwen3-8B
representations, and the LightGCN-profile methods ProEx/ProMax derive much of
their reported strength from full-catalog retrieval and popularity structure
that a 101-candidate sampled panel does not reward. Indeed, a pure popularity
ranking also scores at the random floor in each of the four new domains for
which we measured it (the \textit{Popularity} rows of
Table~\ref{tab:full_official_ndcg10}): because the sampled negatives are
themselves popularity-matched, the protocol deliberately neutralizes the
popularity shortcut, so a row near the floor is not unfairly penalized---it
simply fails to recover user-conditional relevance beyond a popularity prior.
We therefore do not rest the claim on the weakest rows. The informative
comparison is against the strongest baseline that is clearly above the floor:
this is LLMEmb in seven of the eight domains (NDCG@10 $0.094$--$0.274$) and
ProEx in Beauty (NDCG@10 $0.151$). On the six domains where \method{} ranks
first, it improves over the strongest baseline by $+21.6\%$ to $+53.2\%$
NDCG@10, and on the four new domains all 56 per-domain paired tests remain
positive and Holm-significant; on Beauty and Movies the strongest baseline is
ahead, as reported above. The result is thus a robustness claim under a fair
common-denominator reranking protocol, not a statement that these methods are
weak in their native full-catalog setting (see Limitation~5).

\paragraph{Bridge fidelity.} To confirm the unified Qwen3-8B representation
bridge is not itself responsible for the low baseline scores, we re-ran the
strongest SASRec-class baseline, LLM2Rec, in its \emph{native} encoder---an
LLM2Vec model over a Qwen2-0.5B backbone---on the identical same-candidate task,
holding the official LLM2Rec training and scoring fixed and changing only the
item-embedding source. The Qwen3-8B bridge recovers $110\%$ of native NDCG@10 on
Tools and $78\%$ on Sports (pooled $90\%$; HR@10 recovery $116\%$ and $93\%$),
and the bridged baseline stays well above the random floor in both domains. The
bridge therefore preserves most of a baseline's native same-candidate signal
rather than collapsing it, so \method{}'s margin reflects a genuine reranking
difference, not a bridge artifact. (We use a faithful community reproduction of
LLM2Rec, since the authors release code and data but no trained checkpoint, and
validate on the two domains whose native downstream task was prepared; a
full-backbone reproduction of every baseline, e.g.\ LLMEmb, is left to future
work.)

\subsection{Uncertainty as a Reliability Signal}

The observation module asks whether \method{} uncertainty is informative about
ranking reliability before using it as a decision feature. We compute
event-level uncertainty from the candidate-level C-CRP rows, bin events into
five uncertainty quantiles, and compare the lowest and highest bins under the
same ranking records used by the main metric importer. The package audit checks
1,010,000 finite uncertainty rows per domain, exactly 101 candidates per event,
exact candidate-key alignment, and score coverage 1.0.

Table~\ref{tab:uncertainty_stratification} reports the high-minus-low
differences for \method{}. Across all four domains, the high-uncertainty bin is
worse on NDCG@10, MRR, and HR@10. The largest gap appears on Toys
($\Delta$NDCG@10 = -0.3038), while Home and Tools still show clear NDCG@10
drops of -0.0690 and -0.0849. This supports the motivation that the uncertainty
signal stratifies same-candidate ranking reliability.

The module is descriptive. It does not show that manipulating uncertainty
causes a metric change, and it is not a substitute for the official-baseline
comparison in Table~\ref{tab:main_results}. Because events are binned by
\method{}'s own uncertainty and the ranking score is itself a monotone function
of the same posterior, part of this stratification is mechanical; we
therefore read it as confirmation that the uncertainty signal is monotonically
aligned with realized reliability, not as an independent causal effect. This is
consistent with the attribution above: the uncertainty signal is a useful
\emph{descriptor} of where the posterior is reliable, but adding it to the
ranking score does not improve same-candidate ranking.

\input{tables/uncertainty_stratification}

\subsection{Component Ablations}

Table~\ref{tab:module_evidence} summarizes the paper-critical diagnostic
modules. The component ablation is especially important because it prevents a
too-clean story. Using removal-minus-full deltas on NDCG@10, boundary
uncertainty is exactly inert across all four domains (mean delta 0). Removing
counterevidence improves the mean by 0.00168 and is nonworse in 4/4 domains;
removing the risk penalty improves the mean by 0.00082 and is nonworse in 4/4
domains. Removing calibration gap is mixed (mean -0.00078; nonworse in 2/4
domains), and removing evidence support is directionally harmful but small
(mean -0.00013; nonworse in 1/4 domains).

\input{tables/ablation_ndcg10_summary}

The honest conclusion is that the same-candidate ranking gain is carried by the
task-grounded pointwise posterior, while the individual uncertainty components
are weak, redundant, or exactly inert under the frozen configuration. We
therefore report component ablations not as proof that every component is
necessary, but as a characterized negative result: the calibrated-uncertainty
and risk-adjusted ranking family, evaluated as ablations, does not improve
same-candidate ranking over the posterior it is built on.

\subsection{Hyperparameter Stability}

The hyperparameter module evaluates two real controls: the risk exponent
$\eta$ and the uncertainty-weight grid. Validation-selected values are compared
against reporting-only test sweeps on NDCG@10. Both controls are stable within
the pre-registered 5\% relative-drop tolerance in all four domains. For
$\eta$, the validation-selected value matches the test-best value in Sports,
Home, and Tools; Toys selects $\eta=0.25$ on validation while $\eta=0$ is
test-best, but the relative drop is only $1.25\times 10^{-5}$. For the weight
grid, the selected value is test-best on Home and within tolerance on Sports,
Toys, and Tools; the maximum relative drop is $2.97\times 10^{-4}$.

The same result also limits the interpretation. The test-best $\eta$ is zero
in all four domains, so the paper must not claim that a positive risk penalty
is necessary or uniformly beneficial. The correct claim is stability and
sensitivity, not universal optimality.

\input{tables/module_evidence}
